---
title: "Data Visualization"
author: "Daniela Munoz Lopez"
date: "2024-10-22"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#clear environment (RUN EACH TIME SCRIPT IS OPENED)
rm(list = ls())
```

#Load Packages
```{r}
#Load in packages that will be used throughout the markdown.
packages <- c("tidyverse",
                "summarytools",
                "psych",
                "reader",
                "tidyr",
                "lme4",
                "lmerTest",
                "jtools",
                "interactions",
                "rio",
                "ggplot2",
                "dplyr",
                "here")
#invisible(lapply(packages, install.packages, character.only = TRUE)) #install packages (only run once)
invisible(lapply(packages, library, character.only = TRUE)) #load the packages
```

#Load data
```{r}
#load data.
data_dir = here() #Move to the digitalstress_p5_p6 folder (project folder)

data_folder <- "data" #Name of the folder containing the preprocessed data

data_folder_path <- file.path(data_dir, data_folder) #Path to the data within data folder

file_name <- "p5_p6_dss_promis_fully_scored.csv" #Name of the preprocessed data that was created in script1_datacleaning_DML

peru5_6_data <- read.csv(here(data_folder_path,file_name), header = T, sep = ",", na.strings=c("", " ","NA")) #Load data

nrow(peru5_6_data) #N = 973 -- ok: does match N in script 1

#check data
head(peru5_6_data, 20)
tail(peru5_6_data, 20)
```

#All Data
##Histogram of variables
###Age & Grade
```{r}
#Age
hist(peru5_6_data$age_official_confirm,
     main="Participant Age", 
     xlab="Age",
     xlim=c(10, 18))

#Grade
hist(peru5_6_data$grade_2021,
     main="Participant Grade", 
     xlab="Grade",
     xlim=c(6, 11))

#All have a positive skew
```

###Digital Stress
```{r}
#Availability Stress
hist(peru5_6_data$avail_stress,
     main="Availability Stress", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#FOMO
hist(peru5_6_data$fomo,
     main="FOMO", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Approval Anxiety
hist(peru5_6_data$approval_anx,
     main="Approval Anxiety", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Connection Overload
hist(peru5_6_data$connect_overload,
     main="Connection Overload", 
     xlab="Participant Scores",
     xlim=c(1, 5),)

#Online Vigilance
hist(peru5_6_data$online_vigil,
     main="Online Vigilance", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Total DSS
hist(peru5_6_data$dss_total_avg,
     main="Total Digital Stress Average", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#All have a positive skew
```

###PROMIS Anxiety
```{r}
hist(peru5_6_data$promis_anx_sum,
     main="PROMIS Anxiety -- Sum Score", 
     xlab="Participant Scores",
     xlim=c(4, 20))

#Normal distribution -- maybe slight positive skew?
```

###PROMIS Depression
```{r}
hist(peru5_6_data$promis_dep_sum,
     main="PROMIS Depression -- Sum Score", 
     xlab="Participant Scores",
     xlim=c(8, 40))

#Normal distribution -- maybe slight positive skew?
```

##Scatterplot of variables
###Digital Stress
```{r}
#Availability Stress
plot(peru5_6_data$avail_stress,
     main="Availability Stress",
     ylab="Availability Stress Scores",
     ylim=c(1, 5))

#FOMO
plot(peru5_6_data$fomo,
     main="FOMO",
     ylab="FOMO Scores",
     ylim=c(1, 5))

#Approval Anxiety 
plot(peru5_6_data$approval_anx,
     main="Approval Anxiety",
     ylab="Approval Anxiety Scores",
     ylim=c(1, 5))

#Connection Overload
plot(peru5_6_data$connect_overload,
     main="Connection Overload",
     ylab="Connection Overload Scores",
     ylim=c(1, 5))

#Online Vigilance
plot(peru5_6_data$online_vigil,
     main="Online Vigilance",
     ylab="Online Vigilance Scores",
     ylim=c(1, 5))

#Total DSS
plot(peru5_6_data$dss_total_avg,
     main="Total Digital Stress Average",
     ylab="Total Digital Stress Average Scores",
     ylim=c(1, 5))
```

###PROMIS Anxiety
```{r}
plot(peru5_6_data$promis_anx_sum,
     main="PROMIS Anxiety",
     ylab="PROMIS Anxiety -- Sum Score",
     ylim=c(4, 20))
```

###PROMIS Depression
```{r}
plot(peru5_6_data$promis_dep_sum,
     main="PROMIS Depression",
     ylab="PROMIS Depression -- Sum Score",
     ylim=c(8, 40))
```

#Peru 5 Data
##Get data
```{r}
p5 <- peru5_6_data[peru5_6_data$wave == 'Peru 5', ]
```

##Histogram of variables
###Age & Grade
```{r}
#Age
hist(p5$age_official_confirm,
     main="Participant Age", 
     xlab="Age",
     xlim=c(10, 18))

#Grade
hist(p5$grade_2021,
     main="Participant Grade", 
     xlab="Grade",
     xlim=c(6, 11))

#All have a positive skew
```

###Digital Stress
```{r}
#Availability Stress
hist(p5$avail_stress,
     main="Availability Stress", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#FOMO
hist(p5$fomo,
     main="FOMO", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Approval Anxiety
hist(p5$approval_anx,
     main="Approval Anxiety", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Connection Overload
hist(p5$connect_overload,
     main="Connection Overload", 
     xlab="Participant Scores",
     xlim=c(1, 5),)

#Online Vigilance
hist(p5$online_vigil,
     main="Online Vigilance", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Total DSS
hist(p5$dss_total_avg,
     main="Total Digital Stress Average", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#All have a positive skew
```

###PROMIS Anxiety
```{r}
hist(p5$promis_anx_sum,
     main="PROMIS Anxiety -- Sum Score", 
     xlab="Participant Scores",
     xlim=c(4, 20))

#Normal distribution -- maybe slight positive skew?
```

###PROMIS Depression
```{r}
hist(p5$promis_dep_sum,
     main="PROMIS Depression -- Sum Score", 
     xlab="Participant Scores",
     xlim=c(8, 40))

#Normal distribution -- maybe slight positive skew?
```

##Scatterplot of variables
###Digital Stress
```{r}
#Availability Stress
plot(p5$avail_stress,
     main="Availability Stress",
     ylab="Availability Stress Scores",
     ylim=c(1, 5))

#FOMO
plot(p5$fomo,
     main="FOMO",
     ylab="FOMO Scores",
     ylim=c(1, 5))

#Approval Anxiety 
plot(p5$approval_anx,
     main="Approval Anxiety",
     ylab="Approval Anxiety Scores",
     ylim=c(1, 5))

#Connection Overload
plot(p5$connect_overload,
     main="Connection Overload",
     ylab="Connection Overload Scores",
     ylim=c(1, 5))

#Online Vigilance
plot(p5$online_vigil,
     main="Online Vigilance",
     ylab="Online Vigilance Scores",
     ylim=c(1, 5))

#Total DSS
plot(p5$dss_total_avg,
     main="Total Digital Stress Average",
     ylab="Total Digital Stress Average Scores",
     ylim=c(1, 5))
```

###PROMIS Anxiety
```{r}
plot(p5$promis_anx_sum,
     main="PROMIS Anxiety",
     ylab="PROMIS Anxiety -- Sum Score",
     ylim=c(4, 20))
```

###PROMIS Depression
```{r}
plot(p5$promis_dep_sum,
     main="PROMIS Depression",
     ylab="PROMIS Depression -- Sum Score",
     ylim=c(8, 40))
```

#Peru 6 Data
##Get data
```{r}
p6 <- peru5_6_data[peru5_6_data$wave == 'Peru 6', ]
```

##Histogram of variables
###Age & Grade
```{r}
#Age
hist(p6$age_official_confirm,
     main="Participant Age", 
     xlab="Age",
     xlim=c(10, 18))

#Grade
hist(p6$grade_2021,
     main="Participant Grade", 
     xlab="Grade",
     xlim=c(6, 11))

#All have a positive skew
```

###Digital Stress
```{r}
#Availability Stress
hist(p6$avail_stress,
     main="Availability Stress", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#FOMO
hist(p6$fomo,
     main="FOMO", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Approval Anxiety
hist(p6$approval_anx,
     main="Approval Anxiety", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Connection Overload
hist(p6$connect_overload,
     main="Connection Overload", 
     xlab="Participant Scores",
     xlim=c(1, 5),)

#Online Vigilance
hist(p6$online_vigil,
     main="Online Vigilance", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#Total DSS
hist(p6$dss_total_avg,
     main="Total Digital Stress Average", 
     xlab="Participant Scores",
     xlim=c(1, 5))

#All have a positive skew
```

###PROMIS Anxiety
```{r}
hist(p6$promis_anx_sum,
     main="PROMIS Anxiety -- Sum Score", 
     xlab="Participant Scores",
     xlim=c(4, 20))

#Normal distribution -- maybe slight positive skew?
```

###PROMIS Depression
```{r}
hist(p6$promis_dep_sum,
     main="PROMIS Depression -- Sum Score", 
     xlab="Participant Scores",
     xlim=c(8, 40))

#Normal distribution -- maybe slight positive skew?
```

##Scatterplot of variables
###Digital Stress
```{r}
#Availability Stress
plot(p6$avail_stress,
     main="Availability Stress",
     ylab="Availability Stress Scores",
     ylim=c(1, 5))

#FOMO
plot(p6$fomo,
     main="FOMO",
     ylab="FOMO Scores",
     ylim=c(1, 5))

#Approval Anxiety 
plot(p6$approval_anx,
     main="Approval Anxiety",
     ylab="Approval Anxiety Scores",
     ylim=c(1, 5))

#Connection Overload
plot(p6$connect_overload,
     main="Connection Overload",
     ylab="Connection Overload Scores",
     ylim=c(1, 5))

#Online Vigilance
plot(p6$online_vigil,
     main="Online Vigilance",
     ylab="Online Vigilance Scores",
     ylim=c(1, 5))

#Total DSS
plot(p6$dss_total_avg,
     main="Total Digital Stress Average",
     ylab="Total Digital Stress Average Scores",
     ylim=c(1, 5))
```

###PROMIS Anxiety
```{r}
plot(p6$promis_anx_sum,
     main="PROMIS Anxiety",
     ylab="PROMIS Anxiety -- Sum Score",
     ylim=c(4, 20))
```

###PROMIS Depression
```{r}
plot(p6$promis_dep_sum,
     main="PROMIS Depression",
     ylab="PROMIS Depression -- Sum Score",
     ylim=c(8, 40))
```
