---
title: "Data Cleaning of Peru 5 and Peru 6 Data with preprocessed data"
author: "Daniela Munoz Lopez"
date: "2024-07-25"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#clear environment (RUN EACH TIME SCRIPT IS OPENED)
rm(list = ls())
```

#Load Packages
```{r}
#Load in packages that will be used throughout the markdown.
packages <- c("tidyverse",
                "summarytools",
                "psych",
                "reader",
                "tidyr",
                "lme4",
                "lmerTest",
                "jtools",
                "interactions",
                "rio",
                "ggplot2",
                "dplyr",
                "here")
#invisible(lapply(packages, install.packages, character.only = TRUE)) #install packages (only run once)
invisible(lapply(packages, library, character.only = TRUE)) #load the packages
```

#Load All Peru Data
```{r}
#load Peru data.
data_dir = dirname(dirname(here())) #Move out of "digitalstress_p5_p6" folder to the "Peru May 2019" folder

wave_folder <- "peru6" #Name of the wave folder containing all Peru 6 data.

data_folder <- file.path(data_dir, "Waves", wave_folder, "projects",
                         "data_prep", "data", "derivatives") #Path to the data within the wave_folder

file_name <- "peru56_DSS_PROMIS_(PSS)_RT_2023Jan25.csv" #Name of the CSV containing the data that was pre-processed by RT

peru6 <- read.csv(here(data_folder,file_name), header = T, sep = ",", na.strings=c("", " ","NA")) #Load data

as_tibble(peru6) #Convert the data frame into a tibble with class tbl_df

#Select only the data collected during Peru 5 and Peru 6
peru5_6 <- peru6 %>%
  filter(wave== 'Peru 5' | wave == 'Peru 6')

nrow(peru5_6) #Count rows of Peru 5 and Peru 6. N = 1,564

#check data
head(peru5_6, 20)
tail(peru5_6, 20)
```

#Filter & Preprocess Data
##Select relevant data
```{r}
#Select project specific columns
peru5_6_relevant <- peru5_6 %>%
  select(Peru3_4_5_6_ID, wave_ID, wave, session, exclude, group,
          gender, birthmth, birthyr, age_selfreport,
          grade_2021, startdate_formatted, duplicate,
          promis_dep1:promis_dep8, promis_anx1:promis_anx4,
          dss1, dss2, dss3, dss4, dss5, dss6, dss7, dss8, dss9, dss10,
          dss11, dss12, dss13, dss14, dss15, dss16, dss17, dss18,
          dss19, dss20)

nrow(peru5_6_relevant) # N = 1564 after selecting project specific rows

#Remove rows that met initial exclusion criteria (i.e., pilot trials).
peru5_6_exclusion <- peru5_6_relevant %>%
  filter(exclude== 'no')

nrow(peru5_6_exclusion) # N = 1564 after selecting project specific rows

#Select relevant groups (based on those who completed all variables of interest)
peru5_6_group <- peru5_6_exclusion %>%
  filter(group== "Group3")

nrow(peru5_6_group) # N = 1055 after selecting project specific groups (Group 3)

#Select relevant sessions (based on those who completed all variables of interest)
peru5_6_group_session <- peru5_6_group %>%
  filter(session== "survey1_6a11" | session== "survey3_6a11")

nrow(peru5_6_group_session) # N = 1055 after selecting project specific groups AND sessions (sessions 1 & 3)
```

##Check demographics type
```{r}
#Check
typeof(peru5_6_group_session$gender) #currently a character -- change to factor
typeof(peru5_6_group_session$grade_2021) #currently an integer -- ok
typeof(peru5_6_group_session$age_selfreport) #currently a double -- ok
```

##Re-code sex
```{r}
#Re-code sex for future analyse
peru5_6_group_session <- peru5_6_group_session %>%
  dplyr::mutate_at(c('gender'),
  funs(dplyr::recode(., "M"='Male', "F"='Female')))

#Make into a factor
peru5_6_group_session$gender <- as.factor(peru5_6_group_session$gender)

#Check type (should be factor/integer)
typeof(peru5_6_group_session$gender) #now an integer
```

##Confirm age variable & limit ages to greater than 10 and lower than 18 (from chatGPT)
```{r}
#Adapt startdate_formatted format
peru5_6_group_session$startdate_formatted <- as.Date(peru5_6_group_session$startdate_formatted, format = "%Y-%m-%d")

#Get year and month from the survey start date
peru5_6_group_session$survey_year <- as.numeric(format(peru5_6_group_session$startdate_formatted, "%Y"))
peru5_6_group_session$survey_month <- as.numeric(format(peru5_6_group_session$startdate_formatted, "%m"))

#Calculate age at the time the survey was taken
peru5_6_group_session$age_official_confirm <- with(peru5_6_group_session, {
  age_years <- survey_year - birthyr
  # Subtract one year if the survey month is before the birth month
  age_years - ifelse(survey_month < birthmth, 1, 0)
})

#Limit ages to greater than 10 and lower than 18
peru5_6_group_session <- peru5_6_group_session %>%
  filter(age_official_confirm>10&age_official_confirm<18)

#Check sample size after limiting age
nrow(peru5_6_group_session) #N = 1053 (dropped 2 participants due to age restrictions)

#Age average and range (round to the nearest tenth)
mean(peru5_6_group_session$age_official_confirm) #12.9
range(peru5_6_group_session$age_official_confirm, na.rm = FALSE, finite = FALSE) #11 to 17
```

##Make measure items numeric
```{r}
#DSS
peru5_6_numeric <- peru5_6_group_session %>%
  mutate_at(vars(dss1:dss20),~as.numeric(as.character(.)))

#PROMIS ANX
peru5_6_numeric <- peru5_6_numeric %>%
  mutate_at(vars(promis_anx1:promis_anx4),~as.numeric(as.character(.)))

#PROMIS DEP
peru5_6_numeric <- peru5_6_numeric %>%
  mutate_at(vars(promis_dep1:promis_dep8),~as.numeric(as.character(.)))
```

##Match DSS items across Peru 5 and Peru 6 data 
###Adjust Peru 5
```{r}
#IMPORTANT NOTE: DSS items 1-20 were administered in Peru 5, however items 6 and 18 were removed after initial EFA by CG. 
#make DF with only Peru 5 data
p5_only <- peru5_6_numeric[grepl("5_", peru5_6_numeric$wave_ID),]

#Check N
nrow(p5_only) #N for Peru 5 only = 526

#drop items 6 and 18
p5_only <- p5_only[, !(names(p5_only) %in% c("dss6", "dss18"))]
```

###Adjust Peru 6
```{r}
#make DF with only Peru 6 data
p6_only <- peru5_6_numeric[grepl("6_", peru5_6_numeric$wave_ID),]

#Check N
nrow(p6_only) #N for Peru 6 only = 527

#drop items 19 and 20 since there is no data for this
p6_only <- p6_only[, !(names(p6_only) %in% c("dss19", "dss20"))]

#Relabel responses to match Peru 5 DSS (no dss 6 or 18) NOTE: ONLY RUN ONCE TO AVOID ERROR.
p6_only <- p6_only %>%
              rename("dss7" = "dss6",
                      "dss8" = "dss7",
                      "dss9" = "dss8",
                      "dss10" = "dss9",
                      "dss11" = "dss10",
                      "dss12" = "dss11",
                      "dss13" = "dss12",
                      "dss14" = "dss13",
                      "dss15" = "dss14",
                      "dss16" = "dss15",
                      "dss17" = "dss16",
                      "dss19" = "dss17",
                      "dss20" = "dss18")
```

###Combine adjusted Peru 5 and Peru 6 dataframes
```{r}
#Combine dataframes
p5_p6_adjusted <- bind_rows(
  p5_only %>% select(Peru3_4_5_6_ID, wave_ID, wave, session, exclude, group, gender, birthmth, birthyr,
                     age_selfreport, age_official_confirm, grade_2021, startdate_formatted,
                     promis_dep1:promis_dep8, promis_anx1:promis_anx4, dss1:dss20),
  p6_only %>% select(Peru3_4_5_6_ID, wave_ID, wave, session, exclude, group, gender, birthmth, birthyr,
                     age_selfreport, age_official_confirm, grade_2021, startdate_formatted,
                     promis_dep1:promis_dep8, promis_anx1:promis_anx4, dss1:dss20))

#Check new dataframe
head(p5_p6_adjusted)

#Sample size (should be N before splitting sample)
nrow(p5_p6_adjusted) #N = 1053

#Adjust data to long format
p5_p6_adjusted <- p5_p6_adjusted %>%
  arrange(Peru3_4_5_6_ID, group)
```

#Careless Responses & NAs 
##Remove careless DSS responses
```{r}
#call careless package to remove repeated responses for DSS
#Note: chunk won't run without the careless library
library(careless)

#Create a new variable in the DF named careless, which is TRUE if participants have the same value in every column of the measure (DSS only) and FALSE if not to indicate repeated (careless) responses.
p5_p6_adjusted$careless <- ifelse(apply(p5_p6_adjusted[ ,(which(colnames (p5_p6_adjusted) == "dss1")):(which(colnames(p5_p6_adjusted)=="dss20"))], MARGIN=1, function(x) length(unique(as.numeric(x)))) == 1, TRUE, FALSE)

#For participants who reported the same response on items of the DSS measure, label as "NA." We decided not to exclude participants who reported the same response for each item of a sub-scale at this time because sub-scale items are interspersed throughout the DSS questionnaire.
p5_p6_adjusted <- p5_p6_adjusted %>% 
   mutate(
     dss1 = ifelse(
                careless == TRUE,
                          "NA", dss1),
     dss2 = ifelse(
                careless == TRUE, 
                          "NA", dss2),
     dss3 = ifelse(
                careless == TRUE, 
                          "NA", dss3),
     dss4 = ifelse(
                careless == TRUE,
                          "NA", dss4),
     dss5 = ifelse(
                careless == TRUE,
                          "NA", dss5),
     dss7 = ifelse(
                careless == TRUE,
                          "NA", dss7),
     dss8 = ifelse(
                careless == TRUE,
                          "NA", dss8),
     dss9 = ifelse(
                careless == TRUE,
                          "NA", dss9),
     dss10 = ifelse(
                careless == TRUE,
                          "NA", dss10),
     dss11 = ifelse(
                careless == TRUE,
                          "NA", dss11),
     dss12 = ifelse(
                careless == TRUE,
                          "NA", dss12),
     dss13 = ifelse(
                careless == TRUE,
                          "NA", dss13),
     dss14 = ifelse(
                careless == TRUE,
                          "NA", dss14),
     dss15 = ifelse(
                careless == TRUE,
                          "NA", dss15),
     dss16 = ifelse(
                careless == TRUE,
                          "NA", dss16),
     dss17 = ifelse(
                careless == TRUE,
                          "NA", dss17),
     dss19 = ifelse(
                careless == TRUE,
                          "NA", dss19),
     dss20 = ifelse(
                careless == TRUE,
                          "NA", dss20))

#Double check that the measures are still numeric. Previous runs of the code would change the object type, so this step is to make sure that does not happen.
##Make DSS numeric
p5_p6_adjusted <- p5_p6_adjusted%>% 
  mutate_at(vars(dss1:dss20), ~as.numeric(as.character(.)))

##Check
typeof(p5_p6_adjusted$dss1)

#Table summarizing results from the careless package
table(p5_p6_adjusted$careless) #Excluded 55 participants who had careless responses 

#Keep participants who did not respond with the same answer repeatedly (i.e., FALSE careless)
p5_p6_adjusted <- p5_p6_adjusted %>% 
  filter(careless == FALSE) 

#Check new sample size of DF that doesn't include people who had careless responses.
nrow(p5_p6_adjusted) #N = 998, dropped 55 participants with careless responses
```

##Drop NAs
```{r}
#Check sample size before dropping NAs
#Check new sample size
nrow(p5_p6_adjusted) #N = 998

#Count number of NAs IN ANY MEASURE for each participant
p5_p6_adjusted_na_count <- p5_p6_adjusted %>%
  mutate(
    count_all_na = rowSums(is.na(select(.,one_of(c(
      'dss1','dss2', 'dss3', 'dss4', 'dss5',
      'dss7', 'dss8', 'dss9', 'dss10', 'dss11', 'dss12', 
      'dss13', 'dss14', 'dss15', 'dss16', 'dss17', 'dss19', 'dss20', 
      'promis_anx1', 'promis_anx2', 'promis_anx3', 'promis_anx4',
      'promis_dep1', 'promis_dep2', 'promis_dep3', 'promis_dep4','promis_dep5', 'promis_dep6', 'promis_dep7', 'promis_dep8'))))))

#Keep only complete cases with filter. Drop people who had ANY NAs. RATIONALE: Given our large sample size, we are going to keep participants with COMPLETE CASES.
p5_p6_adjusted_no_na <- p5_p6_adjusted_na_count %>% 
  filter(count_all_na <= 0) 

#Check new sample size
nrow(p5_p6_adjusted_no_na) #N = 973, dropped 25 due to NAs
```

#Score items 
##DSS Scoring - Mean Score 
###Availability Stress Score
```{r}
p5_p6_availstress_score <- p5_p6_adjusted_no_na %>%
  mutate(
    avail_stress=rowMeans(select(., dss1, dss19, dss20))
)

#Range
range(p5_p6_availstress_score$avail_stress) #1-5

#Mean
mean(p5_p6_availstress_score$avail_stress) #2.0531

#SD
sd(p5_p6_availstress_score$avail_stress) #0.9025638
```

###Approval Anxiety Score
```{r}
p5_p6_appanx_score <- p5_p6_availstress_score %>%
  mutate(
    approval_anx=rowMeans(select(., dss3, dss7, dss9, dss10))
)

#Range
range(p5_p6_appanx_score$approval_anx) #1-5

#Mean
mean(p5_p6_appanx_score$approval_anx) #2.032117

#SD
sd(p5_p6_appanx_score$approval_anx) #1.125912
```

###FOMO Score
```{r}
p5_p6_fomo_score <- p5_p6_appanx_score %>%
  mutate(
    fomo=rowMeans(select(., dss4, dss5, dss14, dss15))
)

#Range
range(p5_p6_fomo_score$fomo) #1-5

#Mean
mean(p5_p6_fomo_score$fomo) #1.914954

#SD
sd(p5_p6_fomo_score$fomo) #0.9263101
```

###Connection Overload Score
```{r}
p5_p6_overload_score <- p5_p6_fomo_score %>%
  mutate(
    connect_overload=rowMeans(select(., dss11, dss13, dss16))
)

#Range
range(p5_p6_overload_score$connect_overload) #1-5

#Mean
mean(p5_p6_overload_score$connect_overload) #1.913669

#SD
sd(p5_p6_overload_score$connect_overload) #0.8583178
```

###Online vigilance Score
```{r}
p5_p6_vigilance_score <- p5_p6_overload_score %>%
  mutate(
    online_vigil=rowMeans(select(., dss2, dss8, dss12, dss17))
)

#Range
range(p5_p6_vigilance_score$online_vigil) #1-5

#Mean
mean(p5_p6_vigilance_score$online_vigil) #2.490236

#SD
sd(p5_p6_vigilance_score$online_vigil) #0.9763311
```

###Total digital stress score
```{r}
p5_p6_alldss_scored <- p5_p6_vigilance_score %>%
  mutate(
    dss_total_avg=rowMeans(select(., dss1, dss2, dss3, dss4, dss5, dss7, dss8, dss9, dss10,
        dss11, dss12, dss13, dss14, dss15, dss16, dss17, dss19, dss20))
)

#Range
range(p5_p6_alldss_scored$dss_total_avg) #1.055556 4.833333

#Mean
mean(p5_p6_alldss_scored$dss_total_avg) #2.091641

#SD
sd(p5_p6_alldss_scored$dss_total_avg) #0.7585636
```

##PROMIS Anxiety - Sum Score
```{r}
#Sum score
p5_p6_alldss_promisanx_scored <- p5_p6_alldss_scored %>%
  mutate(
    promis_anx_sum=rowSums(select(., promis_anx1:promis_anx4))
)

#Range
range(p5_p6_alldss_promisanx_scored$promis_anx_sum) #4-20

#Mean
mean(p5_p6_alldss_promisanx_scored$promis_anx_sum) #10.86536

#SD
sd(p5_p6_alldss_promisanx_scored$promis_anx_sum) #3.81347
```
#DANNY TO ADADPT
###T-Score PROMIS Anxiety for 

##PROMIS Depression - Sum Score
```{r}
#Sum score
p5_p6_fully_scored <- p5_p6_alldss_promisanx_scored %>%
  mutate(
    promis_dep_sum=rowSums(select(., promis_dep1:promis_dep8))
)

#Range
range(p5_p6_fully_scored$promis_dep_sum) #8-40

#Mean
mean(p5_p6_fully_scored$promis_dep_sum) #20.42549

#SD
sd(p5_p6_fully_scored$promis_dep_sum) #8.362778
```

#Cronbach Alpha of measures 
##Total DSS
```{r}
#Make DSS specific data frame
dss_total <- p5_p6_fully_scored %>%
  select(dss1, dss2, dss3, dss4, dss5, dss7, dss8, dss9, dss10,
         dss11, dss12, dss13, dss14, dss15, dss16, dss17, dss19, dss20)

#Check Alpha
alpha(dss_total) #raw alpha = 0.9292514 = 0.93
```

##Availability Stress
```{r}
#Make DSS - availability stress data frame
dss_avail_stress <- p5_p6_fully_scored %>%
  select(dss1, dss19, dss20)

#check alpha
alpha(dss_avail_stress) #raw alpha = 0.841891 = 0.84
```

##Approval Anxiety
```{r}
#make DSS - approval anxiety specific data frame
dss_approval_anx <- p5_p6_fully_scored %>%
  select(dss3, dss7, dss9, dss10)

#check alpha
alpha(dss_approval_anx) #raw alpha = 0.945593 = 0.95
```

##FOMO
```{r}
#make DSS - FOMO specific data frame
dss_fomo <- p5_p6_fully_scored %>%
  select(dss4, dss5, dss14, dss15)

#check alpha
alpha(dss_fomo) #raw alpha = 0.8731212 = 0.87
```

##Connection Overload
```{r}
#make Connection Overload specific data frame
dss_connect <- p5_p6_fully_scored %>%
  select(dss11, dss13, dss16)

#check alpha
alpha(dss_connect) #raw alpha = 0.7646301 = 0.76
```

##Online Vigilance
```{r}
#make Online Vigilance specific data frame
dss_online <- p5_p6_fully_scored %>%
  select(dss2, dss8, dss12, dss17)

#check alpha
alpha(dss_online) #raw alpha = 0.8340929 = 0.83
```

##PROMIS Anxiety
```{r}
#make PROMIS Anxiety specific data frame
promis_anx_alpha <- p5_p6_fully_scored %>%
  select(promis_anx1:promis_anx4)

#check alpha
alpha(promis_anx_alpha) #raw alpha = 0.7830833 = 0.78
```

##PROMIS Depression
```{r}
#make PROMIS Depression specific data frame
promis_dep_alpha <- p5_p6_fully_scored %>%
  select(promis_dep1:promis_dep8)

#check alpha
alpha(promis_dep_alpha) #raw alpha = 0.940782 = 0.94
```

#DANNY TO ADAPT
#Mental Health Rankings
##PROMIS Anxiety rankings
```{r}
#'severe' if  ≥ 13, 'moderate' if ≥ 8, 'mild' if  ≥ 7, 'normal' if ≥ 0
#From Tobias 
p5_p6_fully_scored <- p5_p6_fully_scored %>%
  mutate(
    promis_anx_ranking=cut(p5_p6_fully_scored$promis_anx_sum , breaks=c(0, 7, 8, 13, 100), right = FALSE, labels = FALSE)
  )

# recodes ranking from int to group titles
p5_p6_fully_scored <- p5_p6_fully_scored %>%
  mutate(promis_anx_ranking = recode(p5_p6_fully_scored$promis_anx_ranking, "1" = "normal", "2" = "mild", "3" = "moderate", "4" = "severe"))
```

##PROMIS Depression rankings
```{r}
#'severe' if  ≥ 27, 'moderate' if ≥ 18, 'mild' if  ≥ 14, 'normal' if ≥ 0
#From Tobias 
p5_p6_fully_scored <- p5_p6_fully_scored %>%
  mutate(
    promis_dep_ranking=cut(p5_p6_fully_scored$promis_dep_sum , breaks=c(0, 14, 18, 27, 100), right = FALSE, labels = FALSE)
  )

# recodes ranking from int to group titles
p5_p6_fully_scored <- p5_p6_fully_scored %>%
  mutate(promis_dep_ranking = recode(p5_p6_fully_scored$promis_dep_ranking, "1" = "normal", "2" = "mild", "3" = "moderate", "4" = "severe"))

```

#Quick stats 
##Sample sizes
```{r}
#Total sample size
nrow(p5_p6_fully_scored) #N = 973

#Peru 5 sample size
nrow(p5_p6_fully_scored[p5_p6_fully_scored$wave == 'Peru 5', ]) #N Peru 5 = 496

#Peru 6 sample size
nrow(p5_p6_fully_scored[p5_p6_fully_scored$wave == 'Peru 6', ]) #N Peru 6 = 477
```

##Percentage sex
###Female % of Full sample
```{r}
total_n <- nrow(p5_p6_fully_scored)
total_n #N = 973

sex_counts <- table(p5_p6_fully_scored$gender)
sex_counts #F = 625, M = 348

sex_percentage <- (sex_counts / total_n) * 100
sex_percentage #Female = 64.23433 = 64.2%
```

###Female % of Peru 5
```{r}
total_n_p5 <- nrow(p5_p6_fully_scored[p5_p6_fully_scored$wave == 'Peru 5', ])
total_n_p5 #N = 496

sex_counts_p5 <- table((p5_p6_fully_scored[p5_p6_fully_scored$wave == 'Peru 5', ])$gender)
sex_counts_p5 #F = 306, M = 190

sex_percentage_p5 <- (sex_counts_p5 / total_n_p5) * 100
sex_percentage_p5 #Female = 61.69355 = 61.7%
```

###Female % of Peru 6
```{r}
total_n_p6 <- nrow(p5_p6_fully_scored[p5_p6_fully_scored$wave == 'Peru 6', ])
total_n_p6 #N = 477

sex_counts_p6 <- table((p5_p6_fully_scored[p5_p6_fully_scored$wave == 'Peru 6', ])$gender)
sex_counts_p6 #F = 319, M = 158

sex_percentage_p6 <- (sex_counts_p6 / total_n_p6) * 100
sex_percentage_p6 #Female = 66.87631 = 66.9%
```

##Age Range, Mean, SD 
###Full Sample
```{r}
#Range age
range(p5_p6_fully_scored$age_official_confirm) #11-17

#Mean age
mean(p5_p6_fully_scored$age_official_confirm) #12.88386

#SD age
sd(p5_p6_fully_scored$age_official_confirm) #1.538222

#Range grade
range(p5_p6_fully_scored$grade_2021) #6-11

#Mean grade
mean(p5_p6_fully_scored$grade_2021) #7.640288

#SD grade
sd(p5_p6_fully_scored$grade_2021) #1.49557
```

###Peru 5 
####Peru 5 data set
```{r}
p5_data <- p5_p6_fully_scored[p5_p6_fully_scored$wave == 'Peru 5', ]
```

####Age & Grade Range, Mean, SD
```{r}
#Range age
range(p5_data$age_official_confirm) #11-17

#Mean age
mean(p5_data$age_official_confirm) #12.64113

#SD age
sd(p5_data$age_official_confirm) #1.501596

#Range grade
range(p5_data$grade_2021) #6-11

#Mean grade
mean(p5_data$grade_2021) #7.627016

#SD grade
sd(p5_data$grade_2021) #1.489355
```

####DSS Range, Mean, SD 
#####Total DSS
```{r}
#Range
range(p5_data$dss_total_avg) #1.055556 - 4.833333

#Mean
mean(p5_data$dss_total_avg) #2.12108

#SD
sd(p5_data$dss_total_avg) #0.7499721
```

#####Availability Stress
```{r}
#Range
range(p5_data$avail_stress) #1 - 5

#Mean
mean(p5_data$avail_stress) #2.188172

#SD
sd(p5_data$avail_stress) #0.91844
```

#####Approval Anxiety
```{r}
#Range
range(p5_data$approval_anx) #1 - 5

#Mean
mean(p5_data$approval_anx) #1.998992

#SD
sd(p5_data$approval_anx) #1.1126
```

#####Connection Overload
```{r}
#Range
range(p5_data$connect_overload) #1 - 5

#Mean
mean(p5_data$connect_overload) #1.936828

#SD
sd(p5_data$connect_overload) #0.8682174
```

#####FOMO
```{r}
#Range
range(p5_data$fomo) #1 - 5

#Mean
mean(p5_data$fomo) #1.890625

#SD
sd(p5_data$fomo) #0.9355535
```

#####Online Vigilance
```{r}
#Range
range(p5_data$online_vigil) #1 - 5

#Mean
mean(p5_data$online_vigil) #2.561492

#SD
sd(p5_data$online_vigil) #0.9562389
```

####PROMIS Anxiety Range, Mean, SD
```{r}
#Range
range(p5_data$promis_anx_sum) #4 - 20

#Mean
mean(p5_data$promis_anx_sum) #10.66331

#SD
sd(p5_data$promis_anx_sum) #3.580185
```

####PROMIS Depression Range, Mean, SD
```{r}
#Range
range(p5_data$promis_dep_sum) #8 - 40

#Mean
mean(p5_data$promis_dep_sum) #19.80847

#SD
sd(p5_data$promis_dep_sum) #8.113439
```

###Peru 6 
####Peru 6 data set
```{r}
p6_data <- p5_p6_fully_scored[p5_p6_fully_scored$wave == 'Peru 6', ]
```

####Age & Grade Range, Mean, SD
```{r}
#Range age
range(p6_data$age_official_confirm) #11-17

#Mean age
mean(p6_data$age_official_confirm) #13.13627

#SD age
sd(p6_data$age_official_confirm) #1.536764

#Range grade
range(p6_data$grade_2021) #6-11

#Mean grade
mean(p6_data$grade_2021) #7.654088

#SD grade
sd(p6_data$grade_2021) #1.503445
```

####DSS Range, Mean, SD 
#####Total DSS
```{r}
#Range
range(p6_data$dss_total_avg) #1.055556 - 4.777778

#Mean
mean(p6_data$dss_total_avg) #2.06103

#SD
sd(p6_data$dss_total_avg) #0.7669835
```

#####Availability Stress
```{r}
#Range
range(p6_data$avail_stress) #1 - 5

#Mean
mean(p6_data$avail_stress) #1.912648

#SD
sd(p6_data$avail_stress) #0.8645745
```

#####Approval Anxiety
```{r}
#Range
range(p6_data$approval_anx) #1 - 5

#Mean
mean(p6_data$approval_anx) #2.066562

#SD
sd(p6_data$approval_anx) #1.139737
```

#####Connection Overload
```{r}
#Range
range(p6_data$connect_overload) #1 - 5

#Mean
mean(p6_data$connect_overload) #1.889588

#SD
sd(p6_data$connect_overload) #0.8481408
```

#####FOMO
```{r}
#Range
range(p6_data$fomo) #1 - 5

#Mean
mean(p6_data$fomo) #1.940252

#SD
sd(p6_data$fomo) #0.9168958
```

#####Online Vigilance
```{r}
#Range
range(p6_data$online_vigil) #1 - 5

#Mean
mean(p6_data$online_vigil) #2.416143

#SD
sd(p6_data$online_vigil) #0.9923771
```

####PROMIS Anxiety Range, Mean, SD
```{r}
#Range 
range(p6_data$promis_anx_sum) #4 - 20

#Mean 
mean(p6_data$promis_anx_sum) #11.07547

#SD 
sd(p6_data$promis_anx_sum) #4.034849
```

####PROMIS Depression Range, Mean, SD
```{r}
#Range 
range(p6_data$promis_dep_sum) #8 - 40

#Mean age
mean(p6_data$promis_dep_sum) #21.06709

#SD age
sd(p6_data$promis_dep_sum) #8.575891
```

#Create and export CSV with filtered data ##Set new data folder path for this project
```{r}
proj_data_dir = here() #Stay in the "digitalstress_p5_p6" folder
project_data_folder <- file.path(proj_data_dir, "data") #Path to the data folder for this project
```

#Create & name the CSV and save it in the data_folder (defined at the beginning of the script)
```{r}
write.csv(p5_p6_fully_scored, here(project_data_folder, "p5_p6_dss_promis_fully_scored.csv"), row.names= FALSE)
```
