---
title: "Age & Sex Models"
author: "Daniela Munoz Lopez"
date: "2024-10-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#clear environment (RUN EACH TIME SCRIPT IS OPENED)
rm(list = ls()) 
```

#Load Packages
```{r}
#Load in packages that will be used throughout the markdown.
packages <- c("tidyverse",
                "summarytools",
                "psych",
                "reader",
                "tidyr",
                "lme4",
                "lmerTest",
                "jtools",
                "interactions",
                "rio",
                "ggplot2",
                "dplyr",
                "here",
                "emmeans")
#invisible(lapply(packages, install.packages, character.only = TRUE)) #install packages (only run once)
invisible(lapply(packages, library, character.only = TRUE)) #load the packages
```

#Load data
```{r}
#load data.
data_dir = here() #Move to the digitalstress_p5_p6 folder (project folder)

data_folder <- "data" #Name of the folder containing the preprocessed data

data_folder_path <- file.path(data_dir, data_folder) #Path to the data within data folder

file_name <- "p5_p6_dss_promis_fully_scored.csv" #Name of the preprocessed data that was created in script1_datacleaning_DML

peru5_6_data <- read.csv(here(data_folder_path,file_name), header = T, sep = ",", na.strings=c("", " ","NA")) #Load data

nrow(peru5_6_data) #N = 973 -- ok: does match N in script 1

#check data
head(peru5_6_data, 20)
tail(peru5_6_data, 20)
```

#Long data, repeated observations (2), aging effects (change over time within participants) & cohort effects (diff between subjects @ baseline), account for correlation between variables since they are repeated
#spaghetti & box plots by time
#mean profiles
#scatterplot matrix of responses at different time points
#mixed effects modeling (fixed [population] & random [individual] effects)



Research questions
1. Do males and females differ in their DSS endorsement over time 
2. Do grades differ in their DSS endorsement over time
3. 

#Recode wave to timepoint 
```{r}
peru5_6_data <- peru5_6_data %>% 
     dplyr::mutate_at(c('wave'), 
               funs(dplyr::recode(., "Peru 5"='Time 1',
                                     "Peru 6"='Time 2')))
```
#Linear models 
##DSS Subscales
```{r}
avail_stress_gen_grade_lm <- lmer(avail_stress ~ wave * gender + (1 | Peru3_4_5_6_ID ), peru5_6_data)
approv_anx_gen_grade_lm <- lmer(approval_anx ~ wave * gender + (1 | Peru3_4_5_6_ID ), peru5_6_data)
fomo_gen_grade_lm <- lmer(fomo ~ wave * gender + (1 | Peru3_4_5_6_ID ), peru5_6_data)
online_vigil_gen_grade_lm <- lmer(online_vigil ~ wave * gender + (1 | Peru3_4_5_6_ID ), peru5_6_data)
connect_over_gen_grade_lm <- lmer(connect_overload ~ wave * gender + (1 | Peru3_4_5_6_ID ), peru5_6_data)
```

###Emmeans of models
```{r}
lsm_plot_availability <- summary(emmeans(avail_stress_gen_grade_lm, ~wave|gender))
lsm_plot_availability$task<- "Availability Stress"

lsm_plot_approval<- summary(emmeans(approv_anx_gen_grade_lm, ~wave|gender))
lsm_plot_approval$task<- "Approval Anxiety"

lsm_plot_fomo <- summary(emmeans(fomo_gen_grade_lm, ~wave|gender))
lsm_plot_fomo$task<-"FOMO"

lsm_plot_vigilance <- summary(emmeans(online_vigil_gen_grade_lm, ~wave|gender))
lsm_plot_vigilance$task<- "Online Vigilance"

lsm_plot_connection <- summary(emmeans(connect_over_gen_grade_lm, ~wave|gender))
lsm_plot_connection$task<-"Connection Overload"
```

###Merge models into one
```{r}
lsm_plots_df <- rbind(lsm_plot_availability, lsm_plot_approval, lsm_plot_fomo, lsm_plot_vigilance, lsm_plot_connection)
```

###Plot models
```{r}
pd <- position_dodge(width = 0.1)
age_gender_plot <- ggplot(data=rbind(lsm_plot_availability, lsm_plot_approval, lsm_plot_fomo, lsm_plot_vigilance, lsm_plot_connection), aes(y = emmean, ymax = emmean+SE, ymin = emmean- SE, x = wave, group = interaction(task, gender), color = gender))
age_gender_plot <- age_gender_plot + geom_line(position=pd, size = 1) + geom_point(size=I(2), position=pd)+ geom_errorbar(width=0.3, position=pd)
age_gender_plot <- age_gender_plot + theme_bw() + xlab("Timepoint") 
age_gender_plot <- age_gender_plot + scale_y_continuous(limit = c(1,5), breaks=seq(1,5), name = "Digital Stress Score")
age_gender_plot <- age_gender_plot + theme(
    plot.background = element_blank()
    ,panel.grid.major = element_blank()
    ,panel.grid.minor = element_blank()
    ,axis.text=element_text(size=10)
    ,axis.title=element_text(size=16,face="bold")
    ,legend.text=element_text(size=11)
    ,legend.justification = c(.50, .05), legend.position = c(.10, .73)
    ,legend.background = element_rect(fill=NULL)
  )
age_gender_plot <- age_gender_plot + guides(colour = guide_legend(override.aes=list(size=1)))
age_gender_plot <- age_gender_plot + labs(color = "Sex")
age_gender_plot <- age_gender_plot + labs(caption = sprintf("N= %s", nrow(peru5_6_data))) #add degrees of freedom to plot
age_gender_plot_confirm <- age_gender_plot + facet_grid(. ~ task) + labs(title = "Digital Stress Across Time Points")
age_gender_plot_confirm
```

###Save plot
```{r}
file.name = (here("output","dss_wave_gender_interactions.tff")) #Setting the save location and file name
ggsave(file.name,plot = last_plot(), dpi = 300, device = "tiff") #Save the plot
```

##PROMIS Anxiety
```{r}
avail_stress_gen_grade_lm <- lm(avail_stress ~ wave + promis_anx_ranking, peru5_6_data)
approv_anx_gen_grade_lm <- lm(approval_anx ~ wave + promis_anx_ranking, peru5_6_data)
fomo_gen_grade_lm <- lm(fomo ~ wave + promis_anx_ranking, peru5_6_data)
online_vigil_gen_grade_lm <- lm(online_vigil ~ wave + promis_anx_ranking, peru5_6_data)
connect_over_gen_grade_lm <- lm(connect_overload ~ wave + promis_anx_ranking, peru5_6_data)
```

##Emmeans
```{r}
lsm_plot_availability <- summary(emmeans(avail_stress_gen_grade_lm, ~wave|promis_anx_ranking))
lsm_plot_availability$task<- "Availability Stress"

lsm_plot_approval <- summary(emmeans(approv_anx_gen_grade_lm, ~wave|promis_anx_ranking))
lsm_plot_approval$task<- "Approval Anxiety"

lsm_plot_fomo <- summary(emmeans(fomo_gen_grade_lm, ~wave|promis_anx_ranking))
lsm_plot_fomo$task<-"FOMO"

lsm_plot_vigilance <- summary(emmeans(online_vigil_gen_grade_lm, ~wave|promis_anx_ranking))
lsm_plot_vigilance$task<- "Online Vigilance"

lsm_plot_connection <- summary(emmeans(connect_over_gen_grade_lm, ~wave|promis_anx_ranking))
lsm_plot_connection$task<-"Connection Overload"

```

##Combine models
```{r}
lsm_plot_confirm_df <- rbind(lsm_plot_availability, lsm_plot_approval, lsm_plot_fomo, lsm_plot_vigilance, lsm_plot_connection) #combine all plots into one table
```

##Plot
```{r}
pd <- position_dodge(width = 0.1)
age_gender_plot <- ggplot(data=rbind(lsm_plot_availability, lsm_plot_approval, lsm_plot_fomo, lsm_plot_vigilance, lsm_plot_connection), aes(y = emmean, ymax = emmean+SE, ymin = emmean- SE, x = wave, group = interaction(task, promis_anx_ranking), color = promis_anx_ranking))
age_gender_plot <- age_gender_plot + geom_line(position=pd, size = 1) + geom_point(size=I(2), position=pd)+ geom_errorbar(width=0.3, position=pd)
age_gender_plot <- age_gender_plot + theme_bw() + xlab("Time Point") 
age_gender_plot <- age_gender_plot + scale_y_continuous(limit = c(1,5), breaks=seq(1,5), name = "Digital Scress Score")
age_gender_plot <- age_gender_plot + theme(
    plot.background = element_blank()
    ,panel.grid.major = element_blank()
    ,panel.grid.minor = element_blank()
    ,axis.text=element_text(size=10)
    ,axis.title=element_text(size=16,face="bold")
    ,legend.text=element_text(size=11)
    ,legend.justification = c(.95, .05), legend.position = c(.17, .60)
    ,legend.background = element_rect(fill=NULL)
  )
age_gender_plot <- age_gender_plot + guides(colour = guide_legend(override.aes=list(size=1)))
age_gender_plot <- age_gender_plot + labs(color = "Anxiety")
age_gender_plot <- age_gender_plot + labs(caption = sprintf("DF: %s", lsm_plot_confirm_df$df)) #add degrees of freedom to plot
age_gender_plot_confirm <- age_gender_plot + facet_grid(. ~ task) + labs(title = "Digital Stress & Anxiety Across Time Points")
age_gender_plot_confirm
```

##Save plot
```{r}
file.name = (here("output","dss_promis_anx_grade_waves.tff")) #Setting the save location and file name
ggsave(file.name,plot = last_plot(), dpi = 300, device = "tiff") #Save the plot
```

##PROMIS Depression
```{r}
avail_stress_gen_grade_lm <- lm(avail_stress ~ wave + promis_dep_ranking, peru5_6_data)
approv_anx_gen_grade_lm <- lm(approval_anx ~ wave + promis_dep_ranking, peru5_6_data)
fomo_gen_grade_lm <- lm(fomo ~ wave + promis_dep_ranking, peru5_6_data)
online_vigil_gen_grade_lm <- lm(online_vigil ~ wave + promis_dep_ranking, peru5_6_data)
connect_over_gen_grade_lm <- lm(connect_overload ~ wave + promis_dep_ranking, peru5_6_data)
```

##Emmeans
```{r}
lsm_plot_availability <- summary(emmeans(avail_stress_gen_grade_lm, ~wave|promis_dep_ranking))
lsm_plot_availability$task<- "Availability Stress"

lsm_plot_approval <- summary(emmeans(approv_anx_gen_grade_lm, ~wave|promis_dep_ranking))
lsm_plot_approval$task<- "Approval Anxiety"

lsm_plot_fomo <- summary(emmeans(fomo_gen_grade_lm, ~wave|promis_dep_ranking))
lsm_plot_fomo$task<-"FOMO"

lsm_plot_vigilance <- summary(emmeans(online_vigil_gen_grade_lm, ~wave|promis_dep_ranking))
lsm_plot_vigilance$task<- "Online Vigilance"

lsm_plot_connection <- summary(emmeans(connect_over_gen_grade_lm, ~wave|promis_dep_ranking))
lsm_plot_connection$task<-"Connection Overload"
```

##Combine models
```{r}
lsm_plot_confirm_df <- rbind(lsm_plot_approval, lsm_plot_availability, lsm_plot_fomo, lsm_plot_connection, lsm_plot_vigilance) #combine all plots into one table
```

##Create plot
```{r}
pd <- position_dodge(width = 0.1)
age_gender_plot <- ggplot(data=rbind(lsm_plot_approval, lsm_plot_availability, lsm_plot_fomo, lsm_plot_connection, lsm_plot_vigilance), aes(y = emmean, ymax = emmean+SE, ymin = emmean- SE, x = wave, group = interaction(task, promis_dep_ranking), color = promis_dep_ranking))
age_gender_plot <- age_gender_plot + geom_line(position=pd, size = 1) + geom_point(size=I(2), position=pd)+ geom_errorbar(width=0.3, position=pd)
age_gender_plot <- age_gender_plot + theme_bw() + xlab("Time Point") 
age_gender_plot <- age_gender_plot + scale_y_continuous(limit = c(1,5), breaks=seq(1,5), name = "Digital Stress Score")
age_gender_plot <- age_gender_plot + theme(
    plot.background = element_blank()
    ,panel.grid.major = element_blank()
    ,panel.grid.minor = element_blank()
    ,axis.text=element_text(size=10)
    ,axis.title=element_text(size=16,face="bold")
    ,legend.text=element_text(size=11)
    ,legend.justification = c(.95, .05), legend.position = c(.17, .60)
    ,legend.background = element_rect(fill=NULL)
  )
age_gender_plot <- age_gender_plot + guides(colour = guide_legend(override.aes=list(size=1)))
age_gender_plot <- age_gender_plot + labs(color = "Depression")
age_gender_plot <- age_gender_plot + labs(caption = sprintf("DF: %s", lsm_plot_confirm_df$df)) #add degrees of freedom to plot
age_gender_plot_confirm <- age_gender_plot + facet_grid(. ~ task) + labs(title = "Digital Stress & Depression Across Time Point")
age_gender_plot_confirm
```

##Save plot
```{r}
file.name = (here("output","dss_promis_dep_grade_waves.tff")) #Setting the save location and file name
ggsave(file.name,plot = last_plot(), dpi = 300, device = "tiff") #Save the plot
```
